---
title: "Welcome!"
description: |
  Welcome to the blog of ASA's Record Linkage Interest Group.
preview: wave.png
author:
  - name: Olivier Binette
    url: https://olivierbinette.github.io
    affiliation: Duke University
date: 12-23-2021
repository_url: https://github.com/recordlinkageig/recordlinkageig.github.io
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 3
---

Welcome! This is the blog of ASA's Record Linkage Interest Group (RLIG).

If you are interested in deterministic and probabilistic record linkage, entity resolution, data fusion, or statistical matching, then this is for you. We hope you become a member of RLIG (it's free) to stay up to date with news and events in our community. You can learn more on our main website at [https://sites.google.com/view/rlig/](https://sites.google.com/view/rlig/).

We hope this blog will help foster community within RLIG. We encourage everyone to contribute. Posts can be short, such as to share interesting papers and associated thoughts, or they can be longer to go into any topic you find interesting. You can comment on posts to get in touch with their authors.

First and foremost, we want this blog to be a welcoming place for all. There is no "right" way to write posts -- express yourself as you like. We want to hear your unique perspective. Reply to comments, welcome feedback, and make connections!

Instructions to write blog posts are below. It might seem a bit overwhelming if you have not worked with these tools before. However, we are here to help. If you'd like to post something but don't want to use R, we'll create the post for you. If you're unsure about any of the steps below, get in touch and we'll provide support. Contact me, [Olivier Binette](https://olivierbinette.github.io/), for any question. I'll be more than happy to help you contribute to the blog.


## Contribute

The blog is based on [Distill for Rmarkdown](https://rstudio.github.io/distill/), an [Rmarkdown](https://rmarkdown.rstudio.com/) extension for scientific and technical writing on the web.

In order to contribute a post to this blog, you will need basic familiarity with git, github, R and Rmarkdown. If you are not familiar with these tools, contact [Olivier Binette](https://olivierbinette.github.io/) to help adapt your blog post. We recommend using [RStudio](https://www.rstudio.com/products/rstudio/) as an IDE for its visual rmarkdown editor and suite of compatible editing features. If you do not have RStudio, you will need to separately install [Pandoc](https://pandoc.org/) to render Rmarkdown documents.


### System configuration

Make sure you have [R](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/products/rstudio/) installed (you can separately install [Pandoc](https://pandoc.org/) instead of RStudio). You will also need to install the following packages in R:

```{r, eval=FALSE}
install.packages(c("rmarkdown", "distill"))
```

### Creating a new post

Follow these steps to create a new post:

1. Fork the repository [https://github.com/recordlinkageig/recordlinkageig.github.io](https://github.com/recordlinkageig/recordlinkageig.github.io).
2. Create a new RStudio project from version control, using the forked repository url. Alternatively, clone the forked repository and `cd` into it.
3. Use the following R command to create a new post:

```{r, eval=FALSE}
distill::create_post("My Post Title")
```

4. This will create a new folder, named after the current date and provided post title, in the `_posts` directory. This folder contains an Rmarkdown document for you to edit.
5. Edit the Rmarkdown document, referring to [https://rstudio.github.io/distill/](https://rstudio.github.io/distill/) for help with formatting and metadata options. You may also use previous posts as templates.
6. Run the following R command to render your blog post as an html file:

```{r, eval=FALSE}
rmarkdown::render_site()
```

7. Commit, push, and create a pull request on [https://github.com/RecordLinkageIG/RecordLinkageIG.github.io](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io).

The pull request will be reviewed before your post is published on RLIG's blog.


### Submission requirements checklist

Make sure to review the following items before submitting your post.

- As part of your article's metadata, you should use the template below to provide:
  - Post title and description
  - Current date
  - Image preview
  - Author information (full name, url/email address, and affiliation)
  
```{r, eval=FALSE}
title: "My Post Title"
description: |
  Description of my post.
preview: http://website.com/post-image
author:
  - name: Full Name
    url: url.com
    affiliation: State University
date: 2022-01-01
```

- At the end of your article, as part of the appendix, you should provide as section titled "About the Author(s)" which contains a short bibliography or some information regarding your background and interests. The goal is introduce you to RLIG's members and to help foster a sense of community. You can use the template below:

```{r, eval=FALSE}
## About the Author(s) {.appendix}

The author works at State University. They are [...].
```

## Code of Conduct

Please note that the RecordLinkageIG.github.io project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.





