---
output: rmarkdown::github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message=FALSE, 
  warning=FALSE
)
```

[![pages-build-deployment](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io/actions/workflows/pages/pages-build-deployment/badge.svg)](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io/actions/workflows/pages/pages-build-deployment) [![render](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io/actions/workflows/R-CMD-check.yaml)

**[recordlinkageig.github.io](https://recordlinkageig.github.io)**

## About

This repository hosts the blog of the American Statistical Association's [Record Linkage Interest Group (RLIG)](https://sites.google.com/view/rlig). 

The blog is open to contributions from anyone with interest in deterministic and probabilistic record linkage, entity resolution, data fusion, and statistical matching. See below for contribution instructions.

```{r}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(magrittr, stringr, dplyr, xml2, lubridate, ggplot2, scales)
```

```{r}
# From https://github.com/shannonpileggi/pipinghotdata_distill
# inspired by Matt Dray's blog 
# https://www.rostrum.blog/2021/04/14/gha-readme/
xml <- read_xml("https://recordlinkageig.github.io/index.xml")
titles <- xml_find_all(xml, ".//title") %>% 
  str_remove_all("<title>|</title>") %>% 
  .[-1]
links <- xml_find_all(xml, ".//link") %>% 
    str_remove_all("<link>|</link>") %>% 
  .[-1]
dates <- links %>% 
  str_remove(".*posts/") %>% 
  str_sub(1, 10)
                      # extract text
# data frame of all posts
posts <- tibble(dates, titles, links)
# number of days since last post
days_last_post <- Sys.Date() - max(lubridate::as_date(dates))
posts_since_2020 <- posts %>% 
  mutate(dates = lubridate::as_date(dates)) %>% 
  filter(dates >= lubridate::as_date("2020-01-01"))
posts_per_month <- scales::number((nrow(posts_since_2020) / (as.numeric(today() - min(posts_since_2020$dates)))) * 30, 0.1)
days_bt_posts <- scales::number((as.numeric(today() - min(posts_since_2020$dates))) / nrow(posts), 1)
```


#### Some stats

- RLIG's blog has **`r nrow(posts)`** posts since **`r min(lubridate::as_date(dates))`**.

- The last post was published **`r days_last_post`** days ago ([`r titles[1]`](`r links[1]`)).


```{r plot-obj, fig.height=1, fig.width=10, dpi=300}
# Create plot object
posts %>%
  ggplot(aes(x = lubridate::as_date(dates), y = 1)) +
  geom_point(shape = "|", size = 5,   color = "#f95355") + 
  theme(
    panel.grid = element_blank(),
    # creates the light gray box around the plot ----
    panel.background = element_rect(fill = "white", color = "white"),
    axis.title = element_blank(),
    axis.text.y = element_blank(),
    axis.text.x = element_text(size = 14),
    axis.ticks = element_blank(),
    plot.margin = margin(0, 10, 0, 10)
  ) +
  ggtitle("Published posts history")
```



<details><summary> Click to expand a full list of posts</summary>

```{r posts-table}
posts %>%
  transmute(
    Date = dates, 
    Title = paste0("[", titles, "](", links, ")")
  ) %>% 
  knitr::kable()
```
</details>


## Contribute

The blog is based on [Distill for Rmarkdown](https://rstudio.github.io/distill/), an [Rmarkdown](https://rmarkdown.rstudio.com/) extension for scientific and technical writing on the web.

In order to contribute a post to this blog, you will need basic familiarity with git, github, R and Rmarkdown. If you are not familiar with these tools, contact [Olivier Binette](https://olivierbinette.github.io/) to help adapt your blog post. We recommend using [RStudio](https://www.rstudio.com/products/rstudio/) as an IDE for its visual rmarkdown editor and suite of compatible editing features. If you do not have RStudio, you will need to separately install [Pandoc](https://pandoc.org/) to render Rmarkdown documents.


### System configuration

Make sure you have [R](https://www.r-project.org/) and [RStudio](https://www.rstudio.com/products/rstudio/) installed (you can separately install [Pandoc](https://pandoc.org/) instead of RStudio). You will also need to install the following packages in R:

```r
install.packages(c("rmarkdown", "distill"))
```

### Creating a new post

Follow these steps to create a new post:

1. Fork this repository.
2. Create a new RStudio project from version control, using the forked repository url. Alternatively, clone the forked repository and `cd` into it.
3. Use the following R command to create a new post:

```r
distill::create_post("My Post Title")
```

4. This will create a new folder, named after the current date and provided post title, in the `_posts` directory. This folder contains an Rmarkdown document for you to edit.
5. Edit the Rmarkdown document, referring to [https://rstudio.github.io/distill/](https://rstudio.github.io/distill/) for help with formatting and metadata options. You may also use previous posts as templates.
6. Run the following R command to render your blog post as an html file:

```r
rmarkdown::render_site()
```

7. Commit, push, and create a pull request on [https://github.com/RecordLinkageIG/RecordLinkageIG.github.io](https://github.com/RecordLinkageIG/RecordLinkageIG.github.io).

The pull request will be reviewed before your post is published on RLIG's blog.


### Submission requirements checklist

Make sure to review the following items before submitting your post.

- As part of your article's metadata, you should use the template below to provide:
  - Post title and description
  - Current date
  - Image preview
  - Author information (full name, url/email address, and affiliation)
  
```md
title: "My Post Title"
description: |
  Description of my post.
preview: http://website.com/post-image
author:
  - name: Full Name
    url: url.com
    affiliation: State University
date: 2022-01-01
```

- At the end of your article, as part of the appendix, you should provide as section titled "About the Author(s)" which contains a short bibliography or some information regarding your background and interests. The goal is introduce you to RLIG's members and to help foster a sense of community. You can use the template below:

```md
## About the Author(s) {.appendix}

The author works at State University. They are [...].
```

## Code of Conduct

Please note that the RecordLinkageIG.github.io project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


*This readme uses code from [https://github.com/shannonpileggi/pipinghotdata_distill](https://github.com/shannonpileggi/pipinghotdata_distill).*


*Updated `r Sys.time()`*